Rank Verification for Exponential Families

### 2016-10-13 verifying-winner.tex
git address updated, arXiv ready

\section*{Reproducibility}
A git repository containing with the code generating the image in this paper is available at \url{https://bitbucket.org/wfithian/verifying-winner}.

>>>>

\section*{Reproducibility}
A git repository containing with the code generating the image in this paper is available at \url{https://github.com/kenhungkk/verifying-winner}.
